Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-24 sattose/paper.tex
Fixed the values slightly

\begin{table}[H]
  \begin{center}
  \caption{Clone relations} \label{table:relations}
  \bigskip
\begin{tabular}{|l|l|l|} \hline
\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
Unrelated          & 13.537           & 39,39               \\ \hline
Same Class          & 8.341            & 24,27               \\ \hline
Sibling            & 5.978            & 17,39               \\ \hline
Same Method         & 2.456            & 7,15                \\ \hline
External Superclass & 2.402            & 6,99                \\ \hline
First Cousin        & 695             & 2,02                \\ \hline
Superclass         & 488             & 1,42                \\ \hline
Common Hierarchy    & 442             & 1,29                \\ \hline
Ancestor           & 28              & 0,08               \\ \hline
\end{tabular}
\end{center}
\end{table}

>>>>

\begin{table}[H]
  \begin{center}
  \caption{Clone relations} \label{table:relations}
  \bigskip
\begin{tabular}{|l|l|l|} \hline
\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
Unrelated          & 13.529           & 39,37               \\ \hline
Same Class          & 8.341            & 24,28               \\ \hline
Sibling            & 5.978            & 17,40               \\ \hline
Same Method         & 2.456            & 7,15                \\ \hline
External Superclass & 2.402            & 6,99                \\ \hline
First Cousin        & 695             & 2,02                \\ \hline
Superclass         & 489             & 1,42                \\ \hline
Common Hierarchy    & 442             & 1,29                \\ \hline
Ancestor           & 28              & 0,08               \\ \hline
\end{tabular}
\end{center}
\end{table}
